Ornaments as indicators of social changes in northeastern Taiwan before and after European colonial period

### 2019-12-15 analysis/paper/paper.Rmd
fix typo in a file name

```{r poisson-linear-model}
ornaments_potsherds <- read.csv(here("analysis", "data", "raw_data", "kwl_Ornament_potsherds.csv"))
## test: can we predict the number of ornaments using the mass of pottery?
# yes, seems like it

# poisson model
fit <- (glm(formula = sum_orna ~ sum_pot,
            family = "poisson",
            data = ornaments_potsherds))

@@

beta <- unname(coef(summary(fit))[,'Estimate'][2])
# how to print with a reasonable number of significant figures:
beta_print <- signif(beta, 4)

>>>>

```{r poisson-linear-model}
ornaments_potsherds <- read.csv(here("analysis", "data", "raw_data", "Kwl_Ornament_potsherds.csv"))
## test: can we predict the number of ornaments using the mass of pottery?
# yes, seems like it

# poisson model
fit <- glm(formula = sum_orna ~ sum_pot,
            family = "poisson",
            data = ornaments_potsherds)

@@

beta <- unname(coef(summary(fit))[,'Estimate'][2])
# how to print with a reasonable number of significant figures:
beta_print <- signif(beta, 4)
```
